Strong lensing selection effects

### 2022-07-11 paper/seleff.tex
caustics of composite model

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{composite_caustics.eps}
\caption{
Caustics of lenses with fixed radial structure and different ellipticity.
The outer curve is the radial caustic, while the inner diamond is the tangential caustic. Sources located outside the caustic are not strongly lensed. Sources that lie in the region enclosed between the two caustics produce three images, while sources inside the tangential caustic produce five images.
The lens model adopted for this experiment consists of a stellar component and a dark matter halo. The two components have the same ellipticity.
}
\end{figure}
